---
title: "Alcohol vs Seat choice"
author: "Cindy Galdamez"
date: "9/23/20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
The back seat consumes the most alcohol and the front seat consumes the least. The middle seat's consuption is in between the other two results.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

Based on the chart, the back seat average of alcoholic drinks is an average of 9.6, the middle seat average is 3.2 and the front seat is 1.8.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```


```{r}
plot(TukeyHSD(model1))
```

Based on the data there is a chance 1 in 10,000 that these results would be all the same again. The 0 interval shows the middle-front areas are the same based on how much alcohol they consume. The middle-back variables are different and so are the front-back results. The back seat still remains as the highest level of alcohol drinkers.

## Conclusions
Based on the charts above, the back seat is drinking nearly 10 times the amount of drinks compared to the front seat and approximately 3 times as many drinks than the middle seat. Based on the inferential graphs, we can conclude that the middle and front row have a relationship consisting of nearly the same results and the back shares no relationship with any of the other results.
